Orchestrating stencils with the Multi-Stencil Framework

### 2017-03-02 ARTICLES/IJPP/articleR1/evaluation.tex
new results + new structure evaluation

\HC{another benchmark to show that with the static version of \llc the problem disappear ?}

@@

\HC{another benchmark with and without fusion fro task parallelization ?}

@@

>>>>

%\HC{another benchmark to show that with the static version of \llc the problem disappear ?}

@@

%\paragraph{\textbf{Fusion}} Finally, we evaluate loop fusions automatically proposed by MSF from the $TSP$ tree of computation kernels. Figure~\ref{fig:fusion} shows the number of iterations per second as a function of the number of cores with and without fusions. This benchmark is performed on FullSWOF2D onto a $500 \times 500$ domain size with $200$ time iterations. As explained in Section~\ref{sect:fusion}, the MSF loop fusion happens at a high level and is most of the time done naturally by a computer scientist. However, for a non computer scientist which write its numerical codes, an automatic proposition of such fusions avoid errors, particularly for a parallel execution. Moreover, one can notice that the performance is clearly improved (around 40\%) by this fusion.
%
%\begin{figure}[!h]\begin{center}
%  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/fusVSbase.pdf}
%  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations, with and without fusions proposed by MSF.}
%  \label{fig:fusion}
%\end{center}\end{figure}
%
%\HC{another benchmark with and without fusion fro task parallelization ?}

@@

\subsection{Fusion evaluation}

\begin{figure}[ht]
\begin{center}
\subfloat[blabla\label{fig:fusion1}]{
\includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
}\\
\hspace{10pt}
\subfloat[blabla\label{fig:fusion2}]{
\includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
}
\end{center}
\caption{blabla}
\label{fig:fusion}
\end{figure}

%\begin{figure}[!h]\begin{center}
%  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
%  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations, with and without fusions proposed by MSF.}
%  \label{fig:fusion}
%\end{center}\end{figure}
%
%\begin{figure}[!h]\begin{center}
%  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
%  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations, with and without fusions proposed by MSF.}
%  \label{fig:fusion}
%\end{center}\end{figure}
